### 2009-10-20 doc/tech_doc/a-rex/arex_tech_doc.tex
fix latex problems in xml schemas

\begin{shaded}
\begin{verbatim}
    <!-{}- A-Rex service -{}->
    <Service name=\char`\"{}a-rex\char`\"{} id=\char`\"{}a-rex\char`\"{}>
      <!-{}- Optional endpoint element is advised in case of multiple IP adresses -{}->
      <arex:endpoint>https://localhost:60000/arex</arex:endpoint>
      <!-{}- Use information generated by identity.map plugin or default provided below -{}->
      <arex:usermap><arex:defaultLocalName>nobody</arex:defaultLocalName></arex:usermap>
      <!-{}- grid-manager part of a-rex requires legacy configuration file.
           Use arc\_arex.conf example or write own. -{}->
      <arex:gmconfig>/etc/arc\_arex.conf</arex:gmconfig>
    </Service>
\end{verbatim}
\end{shaded}

@@

\begin{footnotesize}
\begin{verbatim}
<?xml version=\char`\"{}1.0\char`\"{} encoding=\char`\"{}UTF-8\char`\"{}?>
<xsd:schema
xmlns:xsd=\char`\"{}http://www.w3.org/2001/XMLSchema\char`\"{}
xmlns=\char`\"{}http://www.nordugrid.org/schemas/ArcConfig/2007/arex\char`\"{}
xmlns:arc=\char`\"{}http://www.nordugrid.org/schemas/ArcConfig/2007/arex\char`\"{}
targetNamespace=\char`\"{}http://www.nordugrid.org/schemas/ArcConfig/2007/arex\char`\"{}
elementFormDefault=\char`\"{}qualified\char`\"{}>
  <xsd:complexType name=\char`\"{}endpoint\_Type\char`\"{}>
    <!-{}-
    This element defines URL of A-REX service as seen from outside.
    -{}->
    <xsd:simpleContent>
      <xsd:extension base=\char`\"{}xsd:string\char`\"{}> 
      </xsd:extension>
    </xsd:simpleContent>
  </xsd:complexType>
  <xsd:element name=\char`\"{}endpoint\char`\"{} type=\char`\"{}endpoint\_Type\char`\"{}/>
  <xsd:complexType name=\char`\"{}gmconfig\_Type\char`\"{}>
    <!-{}-
    This element defines path to arc0 Grid Manager configuartion file.
    By default it is /etc/arc.conf.
    -{}->
    <xsd:simpleContent>
      <xsd:extension base=\char`\"{}xsd:string\char`\"{}>
      </xsd:extension>
    </xsd:simpleContent>
  </xsd:complexType>
  <xsd:element name=\char`\"{}gmconfig\char`\"{} type=\char`\"{}gmconfig\_Type\char`\"{}/>
  <xsd:simpleType name=\char`\"{}gmrun\_Type\char`\"{}>
    <!-{}-
    This element defines how grid-manager part of A-Rex is run.
    {*} internal - as a thread inside service container.
    {*} none - no grid-manager is run.
    {*} external - as a separate executable (not supported anymore).
    Default is 'internal'.
    -{}->
    <xsd:restriction base=\char`\"{}xsd:string\char`\"{}>
      <xsd:enumeration value=\char`\"{}internal\char`\"{}/>
      <xsd:enumeration value=\char`\"{}external\char`\"{}/>
      <xsd:enumeration value=\char`\"{}none\char`\"{}/>
    </xsd:restriction>
  </xsd:simpleType>
  <xsd:element name=\char`\"{}gmrun\char`\"{} type=\char`\"{}gmrun\_Type\char`\"{}/>
  <xsd:complexType name=\char`\"{}usermap\_Type\char`\"{}>
    <xsd:sequence>
      <xsd:element name=\char`\"{}defaultLocalName\char`\"{} type=\char`\"{}xsd:string\char`\"{}
                   minOccurs=\char`\"{}0\char`\"{}/>
    </xsd:sequence>
  </xsd:complexType>
  <xsd:element name=\char`\"{}usermap\char`\"{} type=\char`\"{}usermap\_Type\char`\"{}/>
  <!-{}- CommonName attribute of bes-factory. -{}->
  <xsd:element name=\char`\"{}commonName\char`\"{} type=\char`\"{}xsd:string\char`\"{}/>
  <!-{}- LongDescription attribute of bes-factory. -{}->
  <xsd:element name=\char`\"{}longDescription\char`\"{} type=\char`\"{}xsd:string\char`\"{}/>
  <!-{}- Name of Local Resource Management System. -{}->
  <xsd:element name=\char`\"{}LRMSName\char`\"{} type=\char`\"{}xsd:string\char`\"{}/>
  <!-{}-
  Name of Operating System.
  The values are based on the OSType field of the CIM\_OperatingSystem model:
  http://www.dmtf.org/standards/cim/cim\_schema\_v29
  -{}->
  <xsd:element name=\char`\"{}OperatingSystem\char`\"{} type=\char`\"{}xsd:string\char`\"{}/>
</xsd:schema>
\end{verbatim}
\end{footnotesize}

@@

<?xml version=\char`\"{}1.0\char`\"{} encoding=\char`\"{}UTF-8\char`\"{}?>
<wsdl:definitions targetNamespace=\char`\"{}http://www.nordugrid.org/schemas/a-rex\char`\"{}
 xmlns:SOAP-ENV=\char`\"{}http://schemas.xmlsoap.org/soap/envelope/\char`\"{}
 xmlns:SOAP-ENC=\char`\"{}http://schemas.xmlsoap.org/soap/encoding/\char`\"{}
 xmlns:xsi=\char`\"{}http://www.w3.org/2001/XMLSchema-instance\char`\"{}
 xmlns:xsd=\char`\"{}http://www.w3.org/2001/XMLSchema\char`\"{}
 xmlns:soap=\char`\"{}http://schemas.xmlsoap.org/wsdl/soap/\char`\"{}
 xmlns:wsdl=\char`\"{}http://schemas.xmlsoap.org/wsdl/\char`\"{}
 xmlns:wsa=\char`\"{}http://www.w3.org/2005/08/addressing\char`\"{}
 xmlns:bes-factory=\char`\"{}http://schemas.ggf.org/bes/2006/08/bes-factory\char`\"{}
 xmlns:bes-mgmt=\char`\"{}http://schemas.ggf.org/bes/2006/08/bes-management\char`\"{}
 xmlns:deleg=\char`\"{}http://www.nordugrid.org/schemas/delegation\char`\"{}
 xmlns:wsrf-rpw=\char`\"{}http://docs.oasis-open.org/wsrf/rpw-2\char`\"{}
 xmlns:a-rex=\char`\"{}http://www.nordugrid.org/schemas/a-rex\char`\"{}>
  <wsdl:import namespase=\char`\"{}http://schemas.ggf.org/bes/2006/08/bes-factory\char`\"{}
               location=\char`\"{}./bes-factory.wsdl\char`\"{}/>
  <wsdl:import namespase=\char`\"{}http://schemas.ggf.org/bes/2006/08/bes-management\char`\"{}
               location=\char`\"{}./bes-management.wsdl\char`\"{}/>
  <wsdl:import namespase=\char`\"{}http://www.nordugrid.org/schemas/delegation\char`\"{}
               location=\char`\"{}../schemas/delegation.wsdl\char`\"{}/>
  <wsdl:import namespase=\char`\"{}http://docs.oasis-open.org/wsrf/rpw-2\char`\"{}
               location=\char`\"{}http://docs.oasis-open.org/wsrf/rpw-2.wsdl\char`\"{}/>

@@

    <xsd:schema targetNamespace=\char`\"{}http://www.nordugrid.org/schemas/a-rex\char`\"{}>
      <xsd:import namespace=\char`\"{}http://www.w3.org/2005/08/addressing\char`\"{}
                  schemaLocation=\char`\"{}./ws-addr.xsd\char`\"{}/>
      <xsd:simpleType name=\char`\"{}ActivitySubStateType\char`\"{}>
        <xsd:restriction base=\char`\"{}xsd:string\char`\"{}>
          <xsd:enumeration value=\char`\"{}Accepting\char`\"{}/>
          <xsd:enumeration value=\char`\"{}Accepted\char`\"{}/>
          <xsd:enumeration value=\char`\"{}Preparing\char`\"{}/>
          <xsd:enumeration value=\char`\"{}Prepared\char`\"{}/>
          <xsd:enumeration value=\char`\"{}Submitting\char`\"{}/>
          <xsd:enumeration value=\char`\"{}Executing\char`\"{}/>
          <xsd:enumeration value=\char`\"{}Killing\char`\"{}/>
          <xsd:enumeration value=\char`\"{}Executed\char`\"{}/>
          <xsd:enumeration value=\char`\"{}Finishing\char`\"{}/>
          <xsd:enumeration value=\char`\"{}Finished\char`\"{}/>
          <xsd:enumeration value=\char`\"{}Failed\char`\"{}/>
          <xsd:enumeration value=\char`\"{}Deleted\char`\"{}/>
          <xsd:enumeration value=\char`\"{}Pending\char`\"{}/>
          <xsd:enumeration value=\char`\"{}Held\char`\"{}/>

@@

      <xsd:element name=\char`\"{}State\char`\"{} type=\char`\"{}a-rex:ActivitySubStateType\char`\"{}/>
      <xsd:complexType name=\char`\"{}ResourceInformationDocumentType\char`\"{}>

@@

           <xsd:element name=\char`\"{}BESFactory\char`\"{}
                        type=\char`\"{}bes-factory:FactoryResourceAttributesDocumentType\char`\"{}/>
          <xsd:complexType name=\char`\"{}Glue2Resource\char`\"{} minOccurs='0'>

@@

              <xsd:any namespace=\char`\"{}\#\#other\char`\"{} processContents=\char`\"{}lax\char`\"{}
                       minOccurs=\char`\"{}0\char`\"{} maxOccurs=\char`\"{}unbounded\char`\"{}/>

@@

          <xsd:complexType name=\char`\"{}Activities\char`\"{} minOccurs='0'>

@@

              <xsd:complexType name=\char`\"{}Activity\char`\"{} minOccurs='0' maxOccurs='unbounded'>

@@

                  <xsd:element name=\char`\"{}ActivityIdentifier\char`\"{}
                               type=\char`\"{}wsa:EndpointReferenceType\char`\"{}/>
                  <xsd:element ref=\char`\"{}bes-factory:ActivityDocument\char`\"{} minOccurs='0'/>
                  <xsd:complexType name=\char`\"{}Glue2Job\char`\"{} minOccurs='0'>

@@

      <xsd:complexType name=\char`\"{}ChangeActivityStatusRequestType\char`\"{}>

@@

          <xsd:element name=\char`\"{}ActivityIdentifier\char`\"{} type=\char`\"{}wsa:EndpointReferenceType\char`\"{}/>
          <xsd:element name=\char`\"{}OldStatus\char`\"{} type=\char`\"{}bes-factory:ActivityStatusType\char`\"{}
                       minOccurs=\char`\"{}0\char`\"{}/>
          <xsd:element name=\char`\"{}NewStatus\char`\"{} type=\char`\"{}bes-factory:ActivityStatusType\char`\"{}/>

@@

      <xsd:element name=\char`\"{}ChangeActivityStatus\char`\"{}
                   type=\char`\"{}a-rex:ChangeActivityStatusRequestType\char`\"{}/>
      <xsd:complexType name=\char`\"{}ChangeActivityStatusResponseType\char`\"{}>

@@

          <xsd:element name=\char`\"{}NewStatus\char`\"{} type=\char`\"{}bes-factory:ActivityStatusType\char`\"{}/>

@@

      <xsd:element name=\char`\"{}ChangeActivityStatusResponse\char`\"{}
                   type=\char`\"{}a-rex:ChangeActivityStatusResponseType\char`\"{}/>

@@

	  <xsd:element name=\char`\"{}ActivityIdentifier\char`\"{} 
	  	           type=\char`\"{}wsa:EndpointReferenceType\char`\"{} 
	  	           minOccurs=\char`\"{}1\char`\"{} maxOccurs=\char`\"{}1\char`\"{}/>
          <xsd:element ref=\char`\"{}bes-factory:ActivityDocument\char`\"{} minOccurs=\char`\"{}0\char`\"{}/>
	  <xsd:element name=\char`\"{}ForceMigration\char`\"{} type=\char`\"{}xsd:boolean\char`\"{} minOccurs=\char`\"{}0\char`\"{} maxOccurs=\char`\"{}1\char`\"{}/>    
          <xsd:any namespace=\char`\"{}##other\char`\"{} processContents=\char`\"{}lax\char`\"{} minOccurs=\char`\"{}0\char`\"{} maxOccurs=\char`\"{}unbounded\char`\"{}/>        

@@

        <xsd:anyAttribute namespace=\char`\"{}##other\char`\"{} processContents=\char`\"{}lax\char`\"{}/>

@@

      <xsd:complexType name=\char`\"{}MigrateActivityResponseType\char`\"{}>
        <xsd:sequence>
          <xsd:element name=\char`\"{}ActivityIdentifier\char`\"{} type=\char`\"{}wsa:EndpointReferenceType\char`\"{}/>
          <xsd:element ref=\char`\"{}bes-factory:ActivityDocument\char`\"{} minOccurs=\char`\"{}0\char`\"{}/>
          <xsd:any namespace=\char`\"{}##other\char`\"{} processContents=\char`\"{}lax\char`\"{} minOccurs=\char`\"{}0\char`\"{} maxOccurs=\char`\"{}unbounded\char`\"{}/>        
        </xsd:sequence>
        <xsd:anyAttribute namespace=\char`\"{}##other\char`\"{} processContents=\char`\"{}lax\char`\"{}/>
      </xsd:complexType>

      <xsd:element name=\char`\"{}MigrateActivity\char`\"{}
        type=\char`\"{}a-rex:MigrateActivityType\char`\"{}/>
      <xsd:element name=\char`\"{}MigrateActivityResponse\char`\"{}
        type=\char`\"{}a-rex:MigrateActivityResponseType\char`\"{}/>

    </xsd:schema>
  </wsdl:types>
  <wsdl:message name=\char`\"{}ChangeActivityStatusRequest\char`\"{}>
    <wsdl:part name=\char`\"{}ChangeActivityStatusRequest\char`\"{}
               element=\char`\"{}a-rex:ChangeActivityStatus\char`\"{}/>
  </wsdl:message>
  <wsdl:message name=\char`\"{}ChangeActivityStatusResponse\char`\"{}>
    <wsdl:part name=\char`\"{}ChangeActivityStatusResponse\char`\"{}
               element=\char`\"{}a-rex:ChangeActivityStatusResponse\char`\"{}/>
  </wsdl:message>

  <wsdl:message name=\char`\"{}MigrateActivityRequest\char`\"{}>
    <wsdl:part name=\char`\"{}MigrateActivityRequest\char`\"{} 
	element=\char`\"{}a-rex:MigrateActivity\char`\"{}/>
  </wsdl:message>

  <wsdl:message name=\char`\"{}MigrateActivityResponse\char`\"{}>
    <wsdl:part name=\char`\"{}MigrateActivityResponse\char`\"{} 
        element=\char`\"{}a-rex:MigrateActivityResponse\char`\"{}/>
  </wsdl:message>

  <wsdl:portType name=\char`\"{}a-rex\char`\"{}>
    <wsdl:operation name=\char`\"{}ChangeActivityStatus\char`\"{}>

@@

      <wsdl:input name=\char`\"{}ChangeActivityStatusRequest\char`\"{}
        message=\char`\"{}a-rex:ChangeActivityStatusRequest\char`\"{}/>
      <wsdl:output name=\char`\"{}ChangeActivityStatusResponse\char`\"{}
        message=\char`\"{}a-rex:ChangeActivityStatusResponse\char`\"{}/>
      <wsdl:fault name=\char`\"{}NotAuthorizedFault\char`\"{}
        message=\char`\"{}bes-factory:NotAuthorizedFault\char`\"{}
        wsa:Action=\char`\"{}http://schemas.ggf.org/bes/2006/08/bes-factory/BESFactoryPortType/Fault\char`\"{}/>
      <wsdl:fault name=\char`\"{}InvalidActivityIdentifierFault\char`\"{}
        message=\char`\"{}bes-factory:InvalidActivityIdentifierFault\char`\"{}
        wsa:Action=\char`\"{}http://schemas.ggf.org/bes/2006/08/bes-factory/BESFactoryPortType/Fault\char`\"{}/>
      <wsdl:fault name=\char`\"{}CantApplyOperationToCurrentStateFault\char`\"{}
         message=\char`\"{}bes-factory:CantApplyOperationToCurrentStateFault\char`\"{}
         wsa:Action=\char`\"{}http://schemas.ggf.org/bes/2006/08/bes-factory/BESFactoryPortType/Fault\char`\"{}/>
      <wsdl:fault name=\char`\"{}OperationWillBeAppliedEventuallyFault\char`\"{}
         message=\char`\"{}bes-factory:OperationWillBeAppliedEventuallyFault\char`\"{}
         wsa:Action=\char`\"{}http://schemas.ggf.org/bes/2006/08/bes-factory/BESFactoryPortType/Fault\char`\"{}/>

@@

    <wsdl:operation name=\char`\"{}MigrateActivity\char`\"{}>

@@

         name=\char`\"{}MigrateActivity\char`\"{}
         message=\char`\"{}a-rex:MigrateActivityRequest\char`\"{}  

@@

         name=\char`\"{}MigrateActivityResponse\char`\"{}
         message=\char`\"{}a-rex:MigrateActivityResponse\char`\"{}
      <wsdl:fault name=\char`\"{}NotAuthorizedFault\char`\"{} 
         message=\char`\"{}bes-factory:NotAuthorizedFault\char`\"{}
        wsa:Action=\char`\"{}http://schemas.ggf.org/bes/2006/08/bes-factory/BESFactoryPortType/Fault\char`\"{}/>
      <wsdl:fault name=\char`\"{}NotAcceptingNewActivitiesFault\char`\"{} 
         message=\char`\"{}bes-factory:NotAcceptingNewActivitiesFault\char`\"{}
         wsa:Action=\char`\"{}http://schemas.ggf.org/bes/2006/08/bes-factory/BESFactoryPortType/Fault\char`\"{}/>
      <wsdl:fault name=\char`\"{}UnsupportedFeatureFault\char`\"{} 
         message=\char`\"{}bes-factory:UnsupportedFeatureFault\char`\"{}
         wsa:Action=\char`\"{}http://schemas.ggf.org/bes/2006/08/bes-factory/BESFactoryPortType/Fault\char`\"{}/>
      <wsdl:fault name=\char`\"{}InvalidRequestMessageFault\char`\"{}
         message=\char`\"{}bes-factory:InvalidRequestMessageFault\char`\"{}
         wsa:Action=\char`\"{}http://schemas.ggf.org/bes/2006/08/bes-factory/BESFactoryPortType/Fault\char`\"{}/>

@@

  <wsdl:binding name=\char`\"{}a-rex\char`\"{} type=\char`\"{}a-rex:a-rex\char`\"{}>
    <soap:binding style=\char`\"{}document\char`\"{}
                  transport=\char`\"{}http://schemas.xmlsoap.org/soap/http\char`\"{}/>
    <wsdl:operation name=\char`\"{}ChangeActivityStatus\char`\"{}>
      <soap:operation soapAction=\char`\"{}ChangeActivityStatus\char`\"{}/>
      <wsdl:input name=\char`\"{}ChangeActivityStatusRequest\char`\"{}>
         <soap:body use=\char`\"{}literal\char`\"{}/>

@@

      <wsdl:output name=\char`\"{}ChangeActivityStatusResponse\char`\"{}>
         <soap:body use=\char`\"{}literal\char`\"{}/>

@@

      <wsdl:fault name=\char`\"{}NotAuthorizedFault\char`\"{}>
        <soap:fault name=\char`\"{}NotAuthorizedFault\char`\"{} use=\char`\"{}literal\char`\"{} />

@@

      <wsdl:fault name=\char`\"{}InvalidActivityIdentifierFault\char`\"{}>
        <soap:fault name=\char`\"{}InvalidActivityIdentifierFault\char`\"{} use=\char`\"{}literal\char`\"{} />

@@

      <wsdl:fault name=\char`\"{}CantApplyOperationToCurrentStateFault\char`\"{}>
        <soap:fault name=\char`\"{}CantApplyOperationToCurrentStateFault\char`\"{} use=\char`\"{}literal\char`\"{} />

@@

      <wsdl:fault name=\char`\"{}OperationWillBeAppliedEventuallyFault\char`\"{}>
        <soap:fault name=\char`\"{}OperationWillBeAppliedEventuallyFault\char`\"{} use=\char`\"{}literal\char`\"{} />

@@

    <wsdl:operation name=\char`\"{}MigrateActivity\char`\"{}>
      <soap:operation soapAction=\char`\"{}MigrateActivity\char`\"{} /> 
      <wsdl:input name=\char`\"{}MigrateActivity\char`\"{}>
        <soap:body use=\char`\"{}literal\char`\"{} />

@@

      <wsdl:output name=\char`\"{}MigrateActivityResponse\char`\"{}>
        <soap:body use=\char`\"{}literal\char`\"{} />

@@

      <wsdl:fault name=\char`\"{}NotAcceptingNewActivitiesFault\char`\"{}>
        <soap:fault name=\char`\"{}NotAcceptingNewActivitiesFault\char`\"{} use=\char`\"{}literal\char`\"{} />

@@

      <wsdl:fault name=\char`\"{}UnsupportedFeatureFault\char`\"{}>
        <soap:fault name=\char`\"{}UnsupportedFeatureFault\char`\"{} use=\char`\"{}literal\char`\"{} />

@@

      <wsdl:fault name=\char`\"{}InvalidRequestMessageFault\char`\"{}>
        <soap:fault name=\char`\"{}InvalidRequestMessageFault\char`\"{} use=\char`\"{}literal\char`\"{} />

@@

  <wsdl:binding name=\char`\"{}GetResourcePropertyDocument\char`\"{}
                type=\char`\"{}wsrf-rpw:GetResourcePropertyDocument\char`\"{}>
    <soap:binding style=\char`\"{}document\char`\"{}

>>>>

\begin{shaded}
\begin{verbatim}
    <!-- A-Rex service -->
    <Service name="a-rex" id="a-rex">
      <!-- Optional endpoint element is advised in case of multiple IP adresses -->
      <arex:endpoint>https://localhost:60000/arex</arex:endpoint>
      <!-- Use information generated by identity.map plugin or default provided below -->
      <arex:usermap><arex:defaultLocalName>nobody</arex:defaultLocalName></arex:usermap>
      <!-- grid-manager part of a-rex requires legacy configuration file.
           Use arc.conf example or write own. -->
      <arex:gmconfig>/etc/arc.conf</arex:gmconfig>
    </Service>
\end{verbatim}
\end{shaded}

@@

\begin{footnotesize}
\begin{verbatim}
<?xml version="1.0" encoding="UTF-8"?>
<xsd:schema
xmlns:xsd="http://www.w3.org/2001/XMLSchema"
xmlns="http://www.nordugrid.org/schemas/ArcConfig/2007/arex"
xmlns:arc="http://www.nordugrid.org/schemas/ArcConfig/2007/arex"
targetNamespace="http://www.nordugrid.org/schemas/ArcConfig/2007/arex"
elementFormDefault="qualified">
  <xsd:complexType name="endpoint_Type">
    <!--
    This element defines URL of A-REX service as seen from outside.
    -->
    <xsd:simpleContent>
      <xsd:extension base="xsd:string"> 
      </xsd:extension>
    </xsd:simpleContent>
  </xsd:complexType>
  <xsd:element name="endpoint" type="endpoint_Type"/>
  <xsd:complexType name="gmconfig_Type">
    <!--
    This element defines path to arc0 Grid Manager configuartion file.
    By default it is /etc/arc.conf.
    -->
    <xsd:simpleContent>
      <xsd:extension base="xsd:string">
      </xsd:extension>
    </xsd:simpleContent>
  </xsd:complexType>
  <xsd:element name="gmconfig" type="gmconfig_Type"/>
  <xsd:simpleType name="gmrun_Type">
    <!--
    This element defines how grid-manager part of A-Rex is run.
    {*} internal - as a thread inside service container.
    {*} none - no grid-manager is run.
    {*} external - as a separate executable (not supported anymore).
    Default is 'internal'.
    -->
    <xsd:restriction base="xsd:string">
      <xsd:enumeration value="internal"/>
      <xsd:enumeration value="external"/>
      <xsd:enumeration value="none"/>
    </xsd:restriction>
  </xsd:simpleType>
  <xsd:element name="gmrun" type="gmrun_Type"/>
  <xsd:complexType name="usermap_Type">
    <xsd:sequence>
      <xsd:element name="defaultLocalName" type="xsd:string"
                   minOccurs="0"/>
    </xsd:sequence>
  </xsd:complexType>
  <xsd:element name="usermap" type="usermap_Type"/>
  <!-- CommonName attribute of bes-factory. -->
  <xsd:element name="commonName" type="xsd:string"/>
  <!-- LongDescription attribute of bes-factory. -->
  <xsd:element name="longDescription" type="xsd:string"/>
  <!-- Name of Local Resource Management System. -->
  <xsd:element name="LRMSName" type="xsd:string"/>
  <!--
  Name of Operating System.
  The values are based on the OSType field of the CIM_OperatingSystem model:
  http://www.dmtf.org/standards/cim/cim_schema_v29
  -->
  <xsd:element name="OperatingSystem" type="xsd:string"/>
</xsd:schema>
\end{verbatim}
\end{footnotesize}

@@

<?xml version="1.0" encoding="UTF-8"?>
<wsdl:definitions targetNamespace="http://www.nordugrid.org/schemas/a-rex"
 xmlns:SOAP-ENV="http://schemas.xmlsoap.org/soap/envelope/"
 xmlns:SOAP-ENC="http://schemas.xmlsoap.org/soap/encoding/"
 xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance"
 xmlns:xsd="http://www.w3.org/2001/XMLSchema"
 xmlns:soap="http://schemas.xmlsoap.org/wsdl/soap/"
 xmlns:wsdl="http://schemas.xmlsoap.org/wsdl/"
 xmlns:wsa="http://www.w3.org/2005/08/addressing"
 xmlns:bes-factory="http://schemas.ggf.org/bes/2006/08/bes-factory"
 xmlns:bes-mgmt="http://schemas.ggf.org/bes/2006/08/bes-management"
 xmlns:deleg="http://www.nordugrid.org/schemas/delegation"
 xmlns:wsrf-rpw="http://docs.oasis-open.org/wsrf/rpw-2"
 xmlns:a-rex="http://www.nordugrid.org/schemas/a-rex">
  <wsdl:import namespase="http://schemas.ggf.org/bes/2006/08/bes-factory"
               location="./bes-factory.wsdl"/>
  <wsdl:import namespase="http://schemas.ggf.org/bes/2006/08/bes-management"
               location="./bes-management.wsdl"/>
  <wsdl:import namespase="http://www.nordugrid.org/schemas/delegation"
               location="../schemas/delegation.wsdl"/>
  <wsdl:import namespase="http://docs.oasis-open.org/wsrf/rpw-2"
               location="http://docs.oasis-open.org/wsrf/rpw-2.wsdl"/>

@@

    <xsd:schema targetNamespace="http://www.nordugrid.org/schemas/a-rex">
      <xsd:import namespace="http://www.w3.org/2005/08/addressing"
                  schemaLocation="./ws-addr.xsd"/>
      <xsd:simpleType name="ActivitySubStateType">
        <xsd:restriction base="xsd:string">
          <xsd:enumeration value="Accepting"/>
          <xsd:enumeration value="Accepted"/>
          <xsd:enumeration value="Preparing"/>
          <xsd:enumeration value="Prepared"/>
          <xsd:enumeration value="Submitting"/>
          <xsd:enumeration value="Executing"/>
          <xsd:enumeration value="Killing"/>
          <xsd:enumeration value="Executed"/>
          <xsd:enumeration value="Finishing"/>
          <xsd:enumeration value="Finished"/>
          <xsd:enumeration value="Failed"/>
          <xsd:enumeration value="Deleted"/>
          <xsd:enumeration value="Pending"/>
          <xsd:enumeration value="Held"/>

@@

      <xsd:element name="State" type="a-rex:ActivitySubStateType"/>
      <xsd:complexType name="ResourceInformationDocumentType">

@@

           <xsd:element name="BESFactory"
                        type="bes-factory:FactoryResourceAttributesDocumentType"/>
          <xsd:complexType name="Glue2Resource" minOccurs='0'>

@@

              <xsd:any namespace="##other" processContents="lax"
                       minOccurs="0" maxOccurs="unbounded"/>

@@

          <xsd:complexType name="Activities" minOccurs='0'>

@@

              <xsd:complexType name="Activity" minOccurs='0' maxOccurs='unbounded'>

@@

                  <xsd:element name="ActivityIdentifier"
                               type="wsa:EndpointReferenceType"/>
                  <xsd:element ref="bes-factory:ActivityDocument" minOccurs='0'/>
                  <xsd:complexType name="Glue2Job" minOccurs='0'>

@@

      <xsd:complexType name="ChangeActivityStatusRequestType">

@@

          <xsd:element name="ActivityIdentifier" type="wsa:EndpointReferenceType"/>
          <xsd:element name="OldStatus" type="bes-factory:ActivityStatusType"
                       minOccurs="0"/>
          <xsd:element name="NewStatus" type="bes-factory:ActivityStatusType"/>

@@

      <xsd:element name="ChangeActivityStatus"
                   type="a-rex:ChangeActivityStatusRequestType"/>
      <xsd:complexType name="ChangeActivityStatusResponseType">

@@

          <xsd:element name="NewStatus" type="bes-factory:ActivityStatusType"/>

@@

      <xsd:element name="ChangeActivityStatusResponse"
                   type="a-rex:ChangeActivityStatusResponseType"/>

@@

	  <xsd:element name="ActivityIdentifier" 
	  	           type="wsa:EndpointReferenceType" 
	  	           minOccurs="1" maxOccurs="1"/>
          <xsd:element ref="bes-factory:ActivityDocument" minOccurs="0"/>
	  <xsd:element name="ForceMigration" type="xsd:boolean" minOccurs="0" maxOccurs="1"/>    
          <xsd:any namespace="##other" processContents="lax" minOccurs="0" maxOccurs="unbounded"/>        

@@

        <xsd:anyAttribute namespace="##other" processContents="lax"/>

@@

      <xsd:complexType name="MigrateActivityResponseType">
        <xsd:sequence>
          <xsd:element name="ActivityIdentifier" type="wsa:EndpointReferenceType"/>
          <xsd:element ref="bes-factory:ActivityDocument" minOccurs="0"/>
          <xsd:any namespace="##other" processContents="lax" minOccurs="0" maxOccurs="unbounded"/>        
        </xsd:sequence>
        <xsd:anyAttribute namespace="##other" processContents="lax"/>
      </xsd:complexType>

      <xsd:element name="MigrateActivity"
        type="a-rex:MigrateActivityType"/>
      <xsd:element name="MigrateActivityResponse"
        type="a-rex:MigrateActivityResponseType"/>

    </xsd:schema>
  </wsdl:types>
  <wsdl:message name="ChangeActivityStatusRequest">
    <wsdl:part name="ChangeActivityStatusRequest"
               element="a-rex:ChangeActivityStatus"/>
  </wsdl:message>
  <wsdl:message name="ChangeActivityStatusResponse">
    <wsdl:part name="ChangeActivityStatusResponse"
               element="a-rex:ChangeActivityStatusResponse"/>
  </wsdl:message>

  <wsdl:message name="MigrateActivityRequest">
    <wsdl:part name="MigrateActivityRequest" 
	element="a-rex:MigrateActivity"/>
  </wsdl:message>

  <wsdl:message name="MigrateActivityResponse">
    <wsdl:part name="MigrateActivityResponse" 
        element="a-rex:MigrateActivityResponse"/>
  </wsdl:message>

  <wsdl:portType name="a-rex">
    <wsdl:operation name="ChangeActivityStatus">

@@

      <wsdl:input name="ChangeActivityStatusRequest"
        message="a-rex:ChangeActivityStatusRequest"/>
      <wsdl:output name="ChangeActivityStatusResponse"
        message="a-rex:ChangeActivityStatusResponse"/>
      <wsdl:fault name="NotAuthorizedFault"
        message="bes-factory:NotAuthorizedFault"
        wsa:Action="http://schemas.ggf.org/bes/2006/08/bes-factory/BESFactoryPortType/Fault"/>
      <wsdl:fault name="InvalidActivityIdentifierFault"
        message="bes-factory:InvalidActivityIdentifierFault"
        wsa:Action="http://schemas.ggf.org/bes/2006/08/bes-factory/BESFactoryPortType/Fault"/>
      <wsdl:fault name="CantApplyOperationToCurrentStateFault"
         message="bes-factory:CantApplyOperationToCurrentStateFault"
         wsa:Action="http://schemas.ggf.org/bes/2006/08/bes-factory/BESFactoryPortType/Fault"/>
      <wsdl:fault name="OperationWillBeAppliedEventuallyFault"
         message="bes-factory:OperationWillBeAppliedEventuallyFault"
         wsa:Action="http://schemas.ggf.org/bes/2006/08/bes-factory/BESFactoryPortType/Fault"/>

@@

    <wsdl:operation name="MigrateActivity">

@@

         name="MigrateActivity"
         message="a-rex:MigrateActivityRequest"  

@@

         name="MigrateActivityResponse"
         message="a-rex:MigrateActivityResponse"
      <wsdl:fault name="NotAuthorizedFault" 
         message="bes-factory:NotAuthorizedFault"
        wsa:Action="http://schemas.ggf.org/bes/2006/08/bes-factory/BESFactoryPortType/Fault"/>
      <wsdl:fault name="NotAcceptingNewActivitiesFault" 
         message="bes-factory:NotAcceptingNewActivitiesFault"
         wsa:Action="http://schemas.ggf.org/bes/2006/08/bes-factory/BESFactoryPortType/Fault"/>
      <wsdl:fault name="UnsupportedFeatureFault" 
         message="bes-factory:UnsupportedFeatureFault"
         wsa:Action="http://schemas.ggf.org/bes/2006/08/bes-factory/BESFactoryPortType/Fault"/>
      <wsdl:fault name="InvalidRequestMessageFault"
         message="bes-factory:InvalidRequestMessageFault"
         wsa:Action="http://schemas.ggf.org/bes/2006/08/bes-factory/BESFactoryPortType/Fault"/>

@@

  <wsdl:binding name="a-rex" type="a-rex:a-rex">
    <soap:binding style="document"
                  transport="http://schemas.xmlsoap.org/soap/http"/>
    <wsdl:operation name="ChangeActivityStatus">
      <soap:operation soapAction="ChangeActivityStatus"/>
      <wsdl:input name="ChangeActivityStatusRequest">
         <soap:body use="literal"/>

@@

      <wsdl:output name="ChangeActivityStatusResponse">
         <soap:body use="literal"/>

@@

      <wsdl:fault name="NotAuthorizedFault">
        <soap:fault name="NotAuthorizedFault" use="literal" />

@@

      <wsdl:fault name="InvalidActivityIdentifierFault">
        <soap:fault name="InvalidActivityIdentifierFault" use="literal" />

@@

      <wsdl:fault name="CantApplyOperationToCurrentStateFault">
        <soap:fault name="CantApplyOperationToCurrentStateFault" use="literal" />

@@

      <wsdl:fault name="OperationWillBeAppliedEventuallyFault">
        <soap:fault name="OperationWillBeAppliedEventuallyFault" use="literal" />

@@

    <wsdl:operation name="MigrateActivity">
      <soap:operation soapAction="MigrateActivity" /> 
      <wsdl:input name="MigrateActivity">
        <soap:body use="literal" />

@@

      <wsdl:output name="MigrateActivityResponse">
        <soap:body use="literal" />

@@

      <wsdl:fault name="NotAcceptingNewActivitiesFault">
        <soap:fault name="NotAcceptingNewActivitiesFault" use="literal" />

@@

      <wsdl:fault name="UnsupportedFeatureFault">
        <soap:fault name="UnsupportedFeatureFault" use="literal" />

@@

      <wsdl:fault name="InvalidRequestMessageFault">
        <soap:fault name="InvalidRequestMessageFault" use="literal" />

@@

  <wsdl:binding name="GetResourcePropertyDocument"
                type="wsrf-rpw:GetResourcePropertyDocument">
    <soap:binding style="document"
                  transport="http://schemas.xmlsoap.org/soap/http"/>
    <wsdl:operation name="GetResourcePropertyDocument">
